Article title

### 2017-08-03 paper-webserver.tex
ADD: start of second para

% 1. Our specific problem, previous work
We've attempted to build big-data platforms which address both real-time analyses and integrated storage of results. We have previously developed Superphy \cite{whiteside2016superphy}, an online predictive genomics platform targeting \textit{E. coli}.

>>>>

% 1. Our specific problem, previous work
We have previously developed Superphy \cite{whiteside2016superphy}, an online predictive genomics platform targeting \textit{E. coli}.
Superphy integrates pre-computed results with domain-specific metadata to provide real-time analyses of epidemiology relations over thousands of genomes.
To scale Superphy for tens of thousands of genomes and for use by front-line clinicians, software pipelines should run in real-time and existing population-wide analyses should automatically integrate new results.
